Ultra-deep $K_s$-band Imaging of the \textit{Hubble} Frontier Fields

### 2016-06-22 Paper0/ms.tex
Resubmitted

\author{Gabriel B. Brammer\altaffilmark{1},
Danilo Marchesini\altaffilmark{2},
Ivo Labb\'e\altaffilmark{3}, 
Lee Spitler\altaffilmark{4,5}, 
Daniel Lange-Vagle\altaffilmark{1,2},
Elizbeth A. Barker\altaffilmark{1},
Adriano Fontana\altaffilmark{6},
Audrey Galametz\altaffilmark{7},
Anna Ferr\'e-Mateu\altaffilmark{8},
Tadayuki Kodama\altaffilmark{9},
Britt Lundgren\altaffilmark{10},
Nicholas Martis\altaffilmark{2},
Adam Muzzin\altaffilmark{11},
Mauro Stefanon\altaffilmark{3},
Masayuki Tanaka\altaffilmark{8},
Sune Toft\altaffilmark{12},
Arjen van der Wel\altaffilmark{13},
Benedetta Vulcani\altaffilmark{14}, 
Katherine E. Whitaker\altaffilmark{15,16}
}

@@

\altaffiltext{1}{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
\altaffiltext{2}{Physics and Astronomy Department, Tufts University, Medford, MA 02155, USA}
\altaffiltext{3}{Leiden Observatory, Leiden University, NL-2300 RA Leiden, Netherlands}
\altaffiltext{4}{Department of Physics \& Astronomy, Macquarie University, Sydney, NSW 2109, Australia}
\altaffiltext{5}{Australian Astronomical Observatories, PO Box 915 North Ryde NSW 1670, Australia}
\altaffiltext{6}{INAF, Osservatorio Astronomico di Roma, Via Frascati 33, I-00040, Monteporzio, Italy}
\altaffiltext{7}{Max-Planck-Institut fur extraterrestrische Physik (MPE), Giessenbachstr. 1, D-85748 Garching, Germany}
\altaffiltext{8}{Subaru Telescope, 650 N. Aohoku Pl, 96720 Hilo, HI, USA}
\altaffiltext{9}{National Astronomical Observatory of Japan
2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan}
\altaffiltext{10}{Department of Astronomy, University of Wisconsin, Madison, WI 53706, USA}
\altaffiltext{11}{Kavli Institute for Cosmology, Cambridge University, Madingley Rd, Cambridge, UK, CB3 0HA}
\altaffiltext{12}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, DK-2100 Copenhagen, Denmark}
\altaffiltext{13}{Max Planck Institute for Astronomy (MPIA), K\"onigstuhl 17, 69117, Heidelberg, Germany}
\altaffiltext{14}{School of Physics, Tin Alley, University of Melbourne VIC 3010, Australia}
\altaffiltext{15}{Department of Astronomy, University of Massachusetts Amherst, Amherst, MA 01003, USA}
\altaffiltext{16}{Hubble Fellow}

@@

The latest effort to further our knowledge of galaxy formation and evolution is represented by the {\it HST} Frontier Fields (HFF) program (Lotz et al., in prep). The HFF program is a multi-cycle program consisting of $\sim$560 orbits of Director's Discretionary (DD) time that is imaging six deep fields centered on strong lensing galaxy clusters in parallel with six deep blank fields. The primary science goals of the twelve HFF fields are to 1) reveal the population of galaxies at $z=5-10$ that are 10--50 times fainter intrinsically than any presently known, 2) solidify our understanding of the stellar masses and star formation histories of faint galaxies, 3) provide the first statistically meaningful morphological characterization of star-forming galaxies at $z>5$, and 4) find $z>8$ galaxies magnified by the cluster lensing, with some bright enough to make them accessible to spectroscopic follow-up. Along with {\it HST}, the {\it Spitzer Space Telescope} has devoted 1000 hours of DD time to image the HFF fields at 3.6$\mu$m and 4.5$\mu$m with IRAC (Capak et al., in prep).

The Frontier Fields initiative has inspired a number of separate supporting general observer programs, such as deep \textit{HST} ultraviolet imaging (Siana et al., in prep) and grism spectroscopy \citep[GLASS, ][]{treu:glass}, and deep far-infrared imaging with \textit{Herschel} \citep{rawle:16}.  Whereas the main goal of the HFF is to explore the galaxy population in the first billion years of cosmic history, this dataset is also unique for its combination of surveyed area, multiwavelength coverage and depth for studies of galaxy evolution across most of the age of the universe, down to, and including, the redshifts of the targeted galaxy clusters ($z\approx$~0.3--0.5).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   Exposure Map figure
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!t]
\epsscale{1.17}
\plotone{hawkiff_layout.pdf} % Figures/exposure_map.pdf
\caption{Layout of the Frontier Fields $K_s$-band mosaics.  The positions of the \textit{HST} cluster and parallel fields are shown in the blue (ACS optical) and red (WFC3 IR) polygons.  The light blue polygons in the MACS-0717 field show additional wide-field ACS imaging coverage from  programs GO-9722 and GO-10420 \citep[PI: Ebeling;][]{ma:11}.  The area covered by deep imaging in the \textit{Spitzer}/IRAC 3.6 and 4.5\,\mum\ channels is shown in orange, with the cluster fields indicated by the dashed lines.  The \HAWKI\ field of view is perfectly suited (Abell 2744, MACS-0416, Abell S1063 and Abell 370) for simultaneous imaging of the cluster+parallel field pairs, which require two separate pointings with MOSFIRE (MACS-0717 and MACS-1149).  The footprint of additional archival \HAWKI\ coverage of the MACS-1149 field is indicated by the gray square in the lower right panel.\label{fig:layout}}  
\end{figure*}
%%%%%%%%%%%%%%%%

@@

After dividing by the flat, the background of each exposure is determined in a first pass from the simple median of the four exposures that came both immediately before and after it.  The background-subtracted exposures are combined into a mosaic from which objects are detected.  The final refined background of each exposure is determined in a second ``mask pass'' from a median again from the four exposures before and after it but now aggressively masking all pixels that contain flux from the detected objects.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   2MASS comparison
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!t]
\epsscale{1.17}
\plotone{2mass_phot.pdf} % Figures/exposure_map.pdf
\caption{Comparison of bright-star photometry to the 2MASS public catalog.  The photometric calibration of the $K_s$-band images were determined from standard star observations taken concurrently with the science exposures.  The uncertainties shown are taken from the 2MASS catalog; these stars are measured at very high S/N in the deep $K_s$-band mosaics.  \label{fig:2mass}}  
\end{figure}
%%%%%%%%%%%%%

@@

Final mosaics of each field with $0\farcs1$ pixels are drizzled from the input exposures with weights
\begin{equation}
w^{-1} = F^2\cdot B \cdot \mathrm{FWHM}^\alpha / \sqrt{1-e^2}, 
\label{eq:weight}
\end{equation}
where $F$ is the factor to scale the exposure to the photometric system ($F\equiv1$ for the average of exposures in the OB taken under photometric conditions, $F\gtrsim1$ otherwise), $B$ is the measured background, FWHM is the full width at half maximum of stars identified in the field, and $e$ is the ellipticity of the stellar point spread function (PSF).  The parameter $\alpha$ allows for optimizing the image quality of the final mosaic.  Increasing $\alpha$ puts larger weight on the exposures with the best image-quality while effectively ignoring data with poorer seeing; we adopt $\alpha=2$ for a compromise between the image quality and effective exposure time of the final mosaic.

Finally, we subtract a cell-based background from the final mosaics using an algorithm based on that used by SExtractor and SWarp but that provides more aggressive masking of flux in the outer isophotes of bright galaxies. The mosaics are shown in Fig.~\ref{fig:layout}, along with the position of the deep Frontier Fields \textit{HST} imaging fields.  We also compute the robust NMAD scatter \citep{brammer:08} of empty sky pixels within the same cells to empirically calibrate the inverse variance maps that are shown in Fig.~\ref{fig:ivar_mosaics} (see also \S\ref{s:depth}).  The final image and inverse variance mosaics are provided as an ESO Phase 3 data product\footnote{\url{http://www.eso.org/sci/observing/phase3.html}} and are also currently made available at \url{http://gbrammer.github.io/HAWKI-FF/}\XXX{Note to editor/referee, the final products aren't posted yet but the images are available now and the web releases will be complete by the time of publication.}.  The released images are all scaled to a common zeropoint of 26.0 (AB mag), which gives pixel values of order unity faint galaxies near the detection threshold.  In the sections below we describe the characteristics of the mosaics in more detail.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  U-V
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\epsscale{1.17}
\plotone{delta_UV.pdf} % Figures/exposure_map.pdf
\caption{\textit{Left:} Difference in the derived rest-frame $U-V$ colors as a function of photometric redshift for galaxies in the MACS-0416 parallel field, before and after including $K_s$ photometry along with the \textit{HST} and \textit{Spitzer} measurements.  The scatter in the derived $U-V$ colors at $z>2.5$ is large ($\sim$0.2 mag) where the Balmer/4000~\AA\ break is in the gap between \textit{HST} $H_{160}$ and the \textit{Spitzer} IRAC 3.6~\mum\ bands, which is then well constrained by including $K_s$.  This large scatter translates directly into large scatter on other quantities of interest, such as the stellar mass to light ratio and the age of the stellar populations.  The center and right panels show a dramatic example of a galaxy with a strong break between the \textit{HST} and IRAC bands.  Its photometric redshift and $\Delta(U-V)$ color are indicated with the large red star in the left panel.  The addition of the $K_s$ band pinpoints the location of the break and shrinks the photometric redshift uncertainties by a factor of two and suggesting $z_\mathrm{phot} > 3$ (right panel). \label{fig:delta_UV}}  
\end{figure*}

@@

\noindent We gratefully acknowledge funding support from the STScI Director's Discretionary Research Fund. DM acknowledges the support of the Research Corporation for Science Advancement's Cottrell Scholarship, and of the National Science Foundation under Grant No. 1513473. DM and DL-V acknowledge support from program HST-AR-14302, and KEW gratefully acknowledges support by NASA through Hubble Fellowship grant \#HF2-51368, both of which are provided by NASA through a grant from the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Incorporated, under NASA contract NAS5-26555. BV acknowledges the support from an Australian Research Council Discovery Early Career Researcher Award (PD0028506).  This work was supported by NASA Keck PI Data Awards, administered by the NASA Exoplanet Science Institute. Some of the data presented in this study were obtained at the W. M. Keck Observatory from telescope time allocated to the National Aeronautics and Space Administration through the agency's scientific partnership with the California Institute of Technology and the University of California. The Observatory was made possible by the generous financial support of the W. M. Keck Foundation. The authors wish to recognize and acknowledge the very significant cultural role and reverence that the summit of Mauna Kea has always had within the indigenous Hawaiian community. We are most fortunate to have the opportunity to conduct observations from this mountain. This research made use of Astropy, a community-developed core Python package for Astronomy \citep{astropy}, open-source Python modules Numpy, Scipy, Matplotlib, and scikit-image, and NASA's Astrophysics Data System (ADS).  \\

>>>>

\author{Gabriel B. Brammer\altaffilmark{1},
Danilo Marchesini\altaffilmark{2},
Ivo Labb\'e\altaffilmark{3}, 
Lee Spitler\altaffilmark{4,5}, 
Daniel Lange-Vagle\altaffilmark{1,2},
Elizbeth A. Barker\altaffilmark{1},
Masayuki Tanaka\altaffilmark{6},
Adriano Fontana\altaffilmark{7},
Audrey Galametz\altaffilmark{8},
Anna Ferr\'e-Mateu\altaffilmark{9},
Tadayuki Kodama\altaffilmark{6},
Britt Lundgren\altaffilmark{10},
Nicholas Martis\altaffilmark{2},
Adam Muzzin\altaffilmark{11},
Mauro Stefanon\altaffilmark{3},
Sune Toft\altaffilmark{12},
Arjen van der Wel\altaffilmark{13},
Benedetta Vulcani\altaffilmark{14}, 
Katherine E. Whitaker\altaffilmark{15,16}
}

@@

\altaffiltext{1}{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
\altaffiltext{2}{Physics and Astronomy Department, Tufts University, Medford, MA 02155, USA}
\altaffiltext{3}{Leiden Observatory, Leiden University, NL-2300 RA Leiden, Netherlands}
\altaffiltext{4}{Department of Physics \& Astronomy, Macquarie University, Sydney, NSW 2109, Australia}
\altaffiltext{5}{Australian Astronomical Observatories, PO Box 915 North Ryde NSW 1670, Australia}
\altaffiltext{6}{National Astronomical Observatory of Japan 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan}
\altaffiltext{7}{INAF, Osservatorio Astronomico di Roma, Via Frascati 33, I-00040, Monteporzio, Italy}
\altaffiltext{8}{Max-Planck-Institut fur extraterrestrische Physik (MPE), Giessenbachstr. 1, D-85748 Garching, Germany}
\altaffiltext{9}{Subaru Telescope, 650 N. Aohoku Pl, 96720 Hilo, HI, USA}
\altaffiltext{10}{Department of Astronomy, University of Wisconsin, Madison, WI 53706, USA}
\altaffiltext{11}{Kavli Institute for Cosmology, Cambridge University, Madingley Rd, Cambridge, UK, CB3 0HA}
\altaffiltext{12}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, DK-2100 Copenhagen, Denmark}
\altaffiltext{13}{Max Planck Institute for Astronomy (MPIA), K\"onigstuhl 17, 69117, Heidelberg, Germany}
\altaffiltext{14}{School of Physics, Tin Alley, University of Melbourne VIC 3010, Australia}
\altaffiltext{15}{Department of Astronomy, University of Massachusetts Amherst, Amherst, MA 01003, USA}
\altaffiltext{16}{Hubble Fellow}

@@

The latest effort to further our knowledge of galaxy formation and evolution is represented by the {\it HST} Frontier Fields (HFF) program \citep{lotz:16}. The HFF program is a multi-cycle \textit{Hubble} program consisting of 840 orbits of Director's Discretionary (DD) time that is imaging six deep fields centered on strong lensing galaxy clusters in parallel with six deep blank fields. The primary science goals of the twelve HFF fields are to 1) reveal the population of galaxies at $z=5-10$ that are 10--50 times fainter intrinsically than any presently known, 2) solidify our understanding of the stellar masses and star formation histories of faint galaxies, 3) provide the first statistically meaningful morphological characterization of star-forming galaxies at $z>5$, and 4) find $z>8$ galaxies magnified by the cluster lensing, with some bright enough to make them accessible to spectroscopic follow-up. Along with {\it HST}, the {\it Spitzer Space Telescope} has devoted 1000 hours of DD time to image the HFF fields at 3.6$\mu$m and 4.5$\mu$m with IRAC (Capak et al., in prep).

The Frontier Fields initiative is complemented by a number of separate supporting general observer programs, such as deep \textit{HST} ultraviolet imaging (Siana et al., in prep) and grism spectroscopy \citep[GLASS, ][]{treu:glass}, and deep far-infrared imaging with \textit{Herschel} \citep{rawle:16}.  Whereas the main goal of the HFF is to explore the galaxy population in the first billion years of cosmic history, this dataset is also unique for its combination of surveyed area, multiwavelength coverage and depth for studies of galaxy evolution across most of the age of the universe, down to, and including, the redshifts of the targeted galaxy clusters ($z\approx$~0.3--0.5).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   Exposure Map figure
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!t]
\epsscale{1.17}
\plotone{hawkiff_layout.pdf} % Figures/exposure_map.pdf
\caption{Layout of the Frontier Fields $K_s$-band mosaics.  The positions of the \textit{HST} cluster and parallel fields are shown in the blue (ACS optical) and red (WFC3 IR) polygons.  The light blue polygons in the MACS-0717 field show additional wide-field ACS imaging coverage from  programs GO-9722 and GO-10420 \citep[PI: Ebeling;][]{ma:11}.  The area covered by deep imaging in the \textit{Spitzer}/IRAC 3.6 and 4.5\,\mum\ channels is shown in orange, with the cluster fields indicated by the dashed lines.  The \HAWKI\ field of view is perfectly suited (Abell 2744, MACS-0416, Abell S1063 and Abell 370) for simultaneous imaging of the cluster+parallel field pairs, which require two separate pointings with MOSFIRE (MACS-0717 and MACS-1149).  The footprints of the AO-assisted GSAOI $K_s$-band imaging of the Abell 2744 and MACS-0416 fields \citep{schirmer:15} are shown in green and the footprint of additional archival \HAWKI\ coverage of the MACS-1149 field is indicated by the gray square in the lower right panel.\label{fig:layout}}  
\end{figure*}
%%%%%%%%%%%%%%%%

@@

After dividing by the flat, the background of each exposure is determined in a first pass from the simple median of the four exposures that came both immediately before and after it.  The first-pass background-subtracted exposures are combined into a mosaic, and objects are identified as pixels with values greater than five times the robust standard deviation \citep{beers:90} of the combined image.  A buffer with radius 3 pixels is grown around each ``object'' pixel that satisfies this 5$\sigma$ criterion.  The final refined background of each exposure is determined in a second ``mask pass'' from a median again from the four exposures before and after it but now masking all pixels that contain flux from the detected objects.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   2MASS comparison
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!t]
\epsscale{1.17}
\plotone{2mass_phot.pdf} % Figures/exposure_map.pdf
\caption{Comparison of bright-star photometry to the 2MASS public catalog.  The photometric calibration of the $K_s$-band images were determined from standard star observations taken concurrently with the science exposures.  The uncertainties shown are taken from the 2MASS catalog; these stars are measured at very high S/N in the deep $K_s$-band mosaics.  The solid lines and shaded regions show the weighted average and standard deviation of the photometric offsets for each field, with the quantitative values indicated in the labels at the top of the figure.  \label{fig:2mass}}  
\end{figure}
%%%%%%%%%%%%%

@@

Final mosaics of each field with $0\farcs1$ pixels are drizzled from the input exposures with weights \citep[following][]{whitaker:nmbs}
\begin{equation}
w^{-1} = F^2\cdot B \cdot \mathrm{FWHM}^\alpha / \sqrt{1-e^2}, 
\label{eq:weight}
\end{equation}
where $F$ is the factor to scale the exposure to the photometric system ($F\equiv1$ for the average of exposures in the OB taken under photometric conditions, $F\gtrsim1$ otherwise), $B$ is the measured background, FWHM is the full width at half maximum of stars identified in the field, and $e$ is the ellipticity of the stellar point spread function (PSF).  The parameter $\alpha$ allows for optimizing the image quality of the final mosaic.  Increasing $\alpha$ puts larger weight on the exposures with the best image-quality while effectively ignoring data with poorer seeing; we adopt $\alpha=2$ for a compromise between the image quality and effective exposure time of the final mosaic.

Finally, we subtract a cell-based background from the final mosaics using an algorithm based on that used by SExtractor and SWarp but that provides more aggressive masking of flux in the outer isophotes of bright galaxies. The mosaics are shown in Fig.~\ref{fig:layout}, along with the position of the deep Frontier Fields \textit{HST} imaging fields.  We also compute the robust NMAD scatter \citep{brammer:08} of empty sky pixels within the same cells to empirically calibrate the inverse variance maps that are shown in Fig.~\ref{fig:ivar_mosaics} (see also \S\ref{s:depth}).  The final science and inverse variance mosaics of all six fields are provided as ESO Phase 3 data products\footnote{\url{http://www.eso.org/sci/observing/phase3/news.html\#kiff}}.  The released images are all scaled to a common zeropoint of 26.0 (AB mag), which gives pixel values of order unity faint galaxies near the detection threshold.  In the sections below we describe the characteristics of the mosaics in more detail.

@@

The image quality obtained here with HAWK-I demonstrates the excellent natural seeing conditions of the \textit{VLT} site at Cerro Paranal.  We note here that \HAWKI\ will soon be upgraded with a ground layer adaptive optics module \citep[GRAAL;][]{paufique:10}, that will improve the image quality by factors of 1.5--2 over the natural seeing over the wide \HAWKI\ field of view.  \cite{schirmer:15} recently presented deep AO-corrected $K_s$-band imaging of the MACS-0416 cluster field obtained with the Gemini South Adaptive Optics Imager \citep[GSAOI;][]{carrasco:12}.  Thanks to the availability of a bright guide star near the center of the cluster field, GSAOI provided exquisite image quality (FWHM$\sim0\farcs09$) better than even that of \textit{HST} WFC3/IR.  Though somewhat shallower ($K_s\sim$25.6, 5$\sigma$) and covering a smaller field of view ($1\farcm7\times1\farcm8$, Fig.~\ref{fig:layout}) than the \HAWKI\ mosaics, the GSAOI images provide an auspicious demonstration of the power of wide-field AO-corrected imaging for deep extragalactic science.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  U-V
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\epsscale{1.17}
\plotone{delta_UV.pdf} % Figures/exposure_map.pdf
\caption{\textit{Left:} Difference in the derived rest-frame $U-V$ colors as a function of photometric redshift for galaxies in the MACS-0416 parallel field, before and after including $K_s$ photometry along with the \textit{HST} and \textit{Spitzer} measurements.  The scatter in the derived $U-V$ colors (solid black lines) is large at $z>2.5$ ($\sim$0.2 mag) where the Balmer/4000~\AA\ break is in the gap between \textit{HST} $H_{160}$ and the \textit{Spitzer} IRAC 3.6~\mum\ bands, which is then well constrained by including $K_s$.  This large scatter translates directly into large scatter on other quantities of interest, such as the stellar mass to light ratio and the age of the stellar populations.  The center and right panels show a dramatic example of a galaxy with a strong break between the \textit{HST} and IRAC bands.  Its photometric redshift and $\Delta(U-V)$ color are indicated with the large red star in the left panel.  The SED fits (center panel) and derived photometric redshift probability densities (right panel) before and after including the $K_s$-band photometry are shown with gray and blue curves, respectively.  The addition of the $K_s$ band pinpoints the location of the break and shrinks the photometric redshift uncertainties by a factor of two and suggesting $z_\mathrm{phot} > 3$ (right panel). \label{fig:delta_UV}}  
\end{figure*}

@@

\noindent We gratefully acknowledge funding support from the STScI Director's Discretionary Research Fund. DM acknowledges the support of the Research Corporation for Science Advancement's Cottrell Scholarship, and of the National Science Foundation under Grant No. 1513473. DM and DL-V acknowledge support from program HST-AR-14302, and KEW gratefully acknowledges support by NASA through Hubble Fellowship grant \#HF2-51368, both of which are provided by NASA through a grant from the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Incorporated, under NASA contract NAS5-26555. BV acknowledges the support from an Australian Research Council Discovery Early Career Researcher Award (PD0028506).  MT acknowledges the support by JSPS KAKENHI Grant Number JP15K17617.  This work was supported by NASA Keck PI Data Awards, administered by the NASA Exoplanet Science Institute. Some of the data presented in this study were obtained at the W. M. Keck Observatory from telescope time allocated to the National Aeronautics and Space Administration through the agency's scientific partnership with the California Institute of Technology and the University of California. The Observatory was made possible by the generous financial support of the W. M. Keck Foundation. The authors wish to recognize and acknowledge the very significant cultural role and reverence that the summit of Mauna Kea has always had within the indigenous Hawaiian community. We are most fortunate to have the opportunity to conduct observations from this mountain. This research made use of Astropy, a community-developed core Python package for Astronomy \citep{astropy}, open-source Python modules Numpy, Scipy, Matplotlib, and scikit-image, and NASA's Astrophysics Data System (ADS).

Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere 
under ESO programmes 090.A-0458, 092.A-0472, and 095.A-0533.
\\
